My title

### 2024-02-09 outputs/paper/paper.qmd
made bar graph

ggplot(all_states, aes(x = time_period_start, y = learning_model, color = state)) +
  geom_line() +
  labs(title = "Comparison of Learning Models in US States Over Time",
       x = "Time Period Start", y = "Learning Model") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

>>>>

# ggplot(all_states, aes(x = time_period_start, y = learning_model, color = state)) +
#   geom_line() +
#   labs(title = "Comparison of Learning Models in US States Over Time",
#        x = "Time Period Start", y = "Learning Model") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

# ggplot(all_states, aes(x = time_period_start, y = learning_model, group = state, color = state)) +
#   geom_line() +
#   scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) # Rotate x-axis labels if needed
#

learning_model_summary <- all_states %>%
  count(state, learning_model) %>%
  ungroup()

# Plotting with a bar graph
ggplot(learning_model_summary, aes(x = state, y = n, fill = learning_model)) + 
  geom_bar(stat = "identity", position = "dodge") +
  theme_minimal() +
  labs(x = "State", y = "Frequency of Learning Model", fill = "Learning Model", 
       title = "Comparison of Learning Models in US States") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
